---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```



<style>
body {
  font-family: Arial, sans-serif;
  padding: 20px;
}
h2 {
  color: #2a5d84;
}
</style>

## Observations from My Bus Commute

```{r load_data, include=FALSE}
library(tidyverse)
logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vStO3BGdNiwAcfIGBo7jvq-kprbJKZz7Z6xcwIlIi4HBxqDmFNXWx8ovfwpu0KBhnazYogpob13nh0_/pub?output=csv")
latest_data <- logged_data %>%
  rename(
    timestamp = `Timestamp`,
    passengers = `How many passengers were on the bus (approx.)?`,
    driver_mood = `How would you describe the driver's mood?`,
    time_of_day = `What time of day was your bus ride?`
  )
```


```{r summary_values, echo=FALSE}
mean_passengers <- mean(latest_data$passengers, na.rm = TRUE)
max_passengers <- max(latest_data$passengers, na.rm = TRUE)
```


The average number of passengers per bus ride was **`r round(mean_passengers, 1)`**, and the maximum recorded on a single ride was **`r max_passengers`**.




```{r mood_chart, echo=FALSE}
ggplot(latest_data, aes(x = driver_mood)) +
  geom_bar() +
  labs(title = "Driver Mood Distribution", x = "Driver Mood", y = "Frequency")
```


The bar chart above shows how frequently different driver moods were observed.




```{r time_chart, echo=FALSE}
ggplot(latest_data, aes(x = time_of_day)) +
  geom_bar() +
  labs(title = "Bus Rides by Time of Day", x = "Time of Day", y = "Number of Rides")
```


Most bus rides occurred in the `r latest_data %>% count(time_of_day) %>% arrange(desc(n)) %>% slice(1) %>% pull(time_of_day)` period.


